---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# surfcast

<!-- badges: start -->
<!-- badges: end -->

The surfcast package and [app](https://maurolepore.shinyapps.io/surfcast/) make
it easy to find the best place to surf during a given season or month. The data
comes from https://www.surf-forecast.com/.

## Installation

You can install the development version of surfcast with:

``` r
# install.packages("devtools")
devtools::install_github("maurolepore/surfcast")
```

## Example

Use the database [online](https://maurolepore.shinyapps.io/surfcast/). You may
also access the data via a shiny app or directly in R.

```{r example}
library(surfcast)
library(dplyr, warn.conflicts = FALSE)
```

```r
run_app()
```

```{r}
best_conditions
```

```{r}
best_conditions %>% 
  distinct(country) %>% 
  pull()
```

### I'm in Argentina. Where should I go surfing today?

* Today the swell is NE.
* Today the wind is NW.

```{r}
ne <- "north|east"
nw <- "north|west"
# Not
sw <- "south|west"
se <- "south|east"

best_conditions %>%
  filter(country == "Argentina") %>% 
  filter(grepl(ne, tolower(best_swell))) %>%
  filter(!grepl(sw, tolower(best_swell))) %>%
  filter(grepl(nw, tolower(best_wind))) %>% 
  filter(!grepl(se, tolower(best_wind))) %>% 
  select(spot, best_swell, best_wind)
```

