---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# surfcast

<!-- badges: start -->
<!-- badges: end -->

The surfcast package and [app](https://maurolepore.shinyapps.io/surfcast/) make
it easy to find the best place to surf during a given season or month. The data
comes from https://www.surf-forecast.com/.

## Installation

You can install the development version of surfcast with:

``` r
# install.packages("devtools")
devtools::install_github("maurolepore/surfcast")
```

## Example

Use the database [online](https://maurolepore.shinyapps.io/surfcast/). You may
also access the data via a shiny app or directly in R.

```{r example}
library(dplyr, warn.conflicts = FALSE)
library(glue)
library(surfcast)
```

```r
run_app()
```

```{r}
best_conditions
```

```{r}
best_conditions %>% 
  distinct(country) %>% 
  pull()
```

### I'm in Argentina. Where should I go surfing today?

* Today the swell is NE.
* Today the wind is NW.

```{r}
ne <- "north|east"
nw <- "north|west"
# Not
sw <- "south|west"
se <- "south|east"

best_conditions %>%
  filter(country == "argentina") %>% 
  filter(grepl(ne, tolower(best_swell))) %>%
  filter(!grepl(sw, tolower(best_swell))) %>%
  filter(grepl(nw, tolower(best_wind))) %>% 
  filter(!grepl(se, tolower(best_wind)))
```

### I'm going to Chile in July. Should I take my surfboard?

Most spots that work best in July are close to Santiago, one North near
Antofagasta, and one South near Pichilemu. With a 4.3 a 2-h session should feel
from okay (near Antofagasta) to uncomfortable but doable (all other spots).

La Portada (near Antofagasta):

* Average water temperature in July: [15.6 C](https://www.seatemperature.org/south-america/chile/antofagasta-july.htm) on average. 
* Probability of clean conditions: 20%.

Punta de Lobos (near Pichilemu):

* Average water temperature in july: [13.1 C](https://www.seatemperature.org/south-america/chile/pichilemu.htm).
* Probability of clean conditions: 30%. 

Other spots (near Viña del Mar)

* Average water temperature in July: [13.1](https://www.seatemperature.org/south-america/chile/pichilemu.htm)

* Probability of clean conditions: 20%-70%

--

* Which spots work best in July?

```{r echo=FALSE, message=FALSE}
library(tidyverse, warn.conflicts = FALSE)
library(surfcast)

chile_july <- best_conditions %>% 
  filter(country == "chile", best_month == "july")

chile_july %>% 
  select(spot, type, rating)
```

* How do they rank? 

(The top spot gives me maximum probability of having clean surf, that isn't too
small)

```{r echo=FALSE}
chile_july %>% 
  arrange(desc(clean), blown_out, too_small) %>% 
  select(spot, clean, blown_out, too_small)
```

For details see these pages:

```{r results='asis', echo=FALSE}
spot_url <- paste0(surfcast:::base_url(), "/breaks/", chile_july$spot, "\n")
cat(spot_url, sep = "\n")
```

--

What spots work best in June and August? (Maybe they're worth checking too)

```{r echo=FALSE}
best_conditions %>% 
  filter(country == "chile", best_month %in% c("june", "august")) %>% 
  arrange(desc(clean), blown_out, too_small) %>% 
  select(spot, best_month, clean, blown_out, too_small, type, rating)
```

